### 2019-09-27 conflog.tex
adds building layouts, hotel images

\begin{figure}[h]
	\centering	
	\includegraphics[scale=0.2]{illini-union.png}
	\caption{Illini Student Union}
\end{figure}

The Illini Union is capable of hosting the entire technical program. Keeping the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms has at least enough capacity for 42 people and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair and Illini Room C will host the poster sessions. We will keep the space open to allow the poster sessions and career fairs to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from either the Union or Marriott TowneSuites. See Fig.\ref{fig:conf-map} for a map of the proposed conference facilities.\\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{campus_map.png}
	\caption{Map of conference facilities and hotels}
	\label{fig:conf-map}
\end{figure}

\subsection{Hotels and Accommodations}

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. Since this hotel is just beyond walking distance from the main conference activities, regular transportation to and from the Union will be provided during peak commuting hours (8am-10am $\&$ 3pm-5pm). Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm. This will also be the location of the opening ceremony dinner.\\

@@

@@

\begin{tabular}{lccccc}
\hline\hline
\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
\hline\hline
Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
\end{tabular}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

\newpage
\subsection{Travel and Transportation}

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[scale=0.2]{illini-union.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union-inside.jpg}
	\end{subfigure}
	\caption{Illini Student Union}		
\end{figure}

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

\newpage
\subsection{Hotels and Accommodations}

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. Since this hotel is just beyond walking distance from the main conference activities, regular transportation to and from the Union will be provided during peak commuting hours (8am-10am $\&$ 3pm-5pm). Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm. This will also be the location of the opening ceremony dinner.\\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{illini-queen.jpg}
	\caption{Queen Double}		
\end{figure}

@@

{\centering
\begin{tabular}{lccccc}
\hline\hline
\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
\hline\hline
Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
\end{tabular}}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

\subsection{Travel and Transportation}

### 2019-09-27 uiuc.tex
adds building layouts, hotel images

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award twice. It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.

\subsection{UIUC ANS Student Chapter (ANS-UIUC)}
The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. One of our most popular outreach programs is Engineering Open House (EOH), during which ANS won best exhibit.  EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.

\begin{wrapfigure}{l}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{eoh1.JPG}
    \caption{Mouse Trap Chain Reaction at EOH 2019}
  \end{center}
\end{wrapfigure}

Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC. Events range from tours of various facilities to pizza with campus visitors. Some of the past tours have included Clinton Power Station, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.

@@

@@

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.4\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.38\textwidth]{hidra.png}
    \caption{HIDRA}
  \end{center}
\end{wrapfigure}
The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, three new faculty members have been added to this area including: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016.

>>>>

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.44\textwidth]{alma.jpg}
  \end{center}
\end{wrapfigure}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award twice. It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.

\subsection{UIUC ANS Student Chapter (ANS-UIUC)}

The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. One of our most popular outreach programs is Engineering Open House (EOH), during which ANS won best exhibit.  EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC. Events range from tours of various facilities to pizza with campus visitors. Some of the past tours have included Clinton Power Station, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.15]{eoh1.JPG}
  \caption{Mouse Trap Chain Reaction at EOH 2019}
\end{figure}

@@

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{hidra.png}
    \caption{HIDRA}
  \end{center}
\end{wrapfigure}
The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, three new faculty members have been added to this area including: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016.
